Reconciler: A Workflow for writing Reproducible Computational Research Papers

### 2020-07-26 ms.tex
simplify repo
change filename convention to hyphen
fix github action versions

\begin{document}
\DTLloaddb{keys_values}{keys_values.csv}

\title{Reconciler: A Workflow for Certifying Computational Research Reproducibility}

@@

				child{node[draw, anchor=west, fill=red!20]{paper}

@@

				child{node[draw, anchor=west, fill=red!20]{ms.bib}}
				};

@@

\begin{figure}[h]
	\includegraphics[width=\linewidth]{images/image.pdf}
	\caption{Image example created from results code.}
	\label{fig:image}
\end{figure}

@@

\begin{table}[h]
	\centering
	\caption{Table example created from results code.}
	\label{table:table}
	\setlength\tabcolsep{4.2pt}
	\input{tables/table.tex}
\end{table}

>>>>

\begin{document}
\DTLloaddb{keys_values}{results/keys-values.csv}

\title{Reconciler: A Workflow for writing Reproducible Computational Research Papers}

@@

@@

				child{node[draw, anchor=west, fill=red!20]{ms.bib}};

@@

\begin{figure}[h]
	\includegraphics[width=\linewidth]{results/image.pdf}
	\caption{Image example created from results code.}
	\label{fig:image}
\end{figure}

@@

\begin{table}[h]
	\centering
	\caption{Table example created from results code.}
	\label{table:table}
	\setlength\tabcolsep{4.2pt}
	\input{results/table.tex}
\end{table}
